Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-18 manuscript.Rmd
age graphs

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(patchwork)
library(tidyverse)
library(rstatix)
```

@@

@@

```{r part2overall, warning=FALSE, fig.cap="Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant.", fig.align="center", fig.width=7, fig.height=6.5}

@@

```{r, pt2overalltable}
pt2corr_with_outliers <- map_dfc(agree, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree, ~ .x %>% filter_outliers %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

#Overall
group_agree_cor <- cor_test(agree$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree$group %>% filter_outliers %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree$split %>% filter_outliers %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5)

@@

#Bins
pt2corr_with_outliers <- map_dfc(agree_bins, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree_bins, ~ .x %>% filter_outliers %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

group_agree_cor <- cor_test(agree_bins$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree_bins$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree_bins$group %>% filter_outliers %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree_bins$split %>% filter_outliers %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5)

difference_plot <- function(ds) {
  ds <- mutate(ds, diff = prop_human - prop_model)
  ggplot(filter_outliers(ds), aes(x = pos, y = diff, color = pos, group = file)) +
  geom_rect(aes(xmin = "Held", xmax = "Upright",ymin = -.1, ymax = .1), fill = "#e5e5e5", color = "#e5e5e5") + 
  stat_summary(position = position_dodge(.4), alpha = .7) +
  stat_summary(data = filter(ds, file %in% outlier_files), position = position_dodge(.4), aes(shape = file), alpha = .7, color = "#333333") +
  scale_color_manual(values = pal, guide = "none") +
  scale_shape_discrete(guide = "none") + 
  coord_cartesian(ylim = c(-1, 1)) + xlab("") + 
  scale_y_continuous(name = "Prediction Difference (min)", breaks = seq(-1, 1, .2), labels = seq(-10, 10, 2), minor_breaks = waiver()) + 
    theme(axis.text.x = element_text(size = 13, color = "black"))
}
difference_plots <- map(agree_bins, ~ difference_plot(.x))
difference_plots <- map2(difference_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))
difference_plots[[1]] + difference_plots[[2]]

>>>>

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(patchwork)
library(scales)
library(tidyverse)
library(rstatix)
```

@@

```{r timelines, warning=FALSE, fig.cap="Timelines", fig.align="center", fig.width=7.75, fig.height=8}
fullday <- read_csv("data/imu-compiled.csv") %>% 
  mutate(id_uni = factor(id*100+session),
         group = factor(ifelse(age <= 8, "Younger", "Older")),
         nap_time = ifelse(is.na(sit_time), nap_time, NA))
fullday_long <- fullday %>% pivot_longer(cols = nap_time:upright_time, names_to = "position", values_to = "prop") %>% 
  mutate(Position = factor(position,
                           levels = c("nap_time","upright_time", "sit_time", "prone_time", "supine_time", "held_time"),
                           labels = c("Nap","Upright", "Sitting", "Prone", "Supine", "Held"))) %>% 
  arrange(Position, age)

timelines <- function(ds) {
  ggplot(ds, aes(x = clock_time_start, y = prop, fill = Position)) + 
  geom_bar(stat = "identity") + 
  facet_wrap("id_uni",ncol = 1, strip.position = "left") + 
  scale_fill_manual(values = c("Nap" = "gray",pal)) + 
  scale_x_time(breaks = breaks_width("2 hour"), name = "", minor_breaks = waiver()) + 
  theme(legend.position = "bottom", 
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 10, color = "black", angle = 315, hjust = -.15),
        strip.background = element_blank(),
        strip.text.y = element_blank()) + ylab("")
}

timeline_plots <- map(c("Younger", "Older"), ~ timelines(filter(fullday_long, group == .x)))
timeline_plots <- map2(timeline_plots, c("A. 4-7 Months", "B. 11-14 Months"), ~ .x + ggtitle(.y))
timeline_plots[[1]] + timeline_plots[[2]]

@@

```{r part2overall, warning=FALSE, fig.cap="Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant. The three outlier participants are plotted in dark gray, with a different shape marking each individual.", fig.align="center", fig.width=7, fig.height=6.5}

@@

```{r, pt2overalltable}
#By posture
pt2corr_with_outliers <- map_dfc(agree, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree, ~ .x %>% filter_outliers %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

#Overall
group_agree_cor <- cor_test(agree$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree$group %>% filter_outliers %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree$split %>% filter_outliers %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5, caption = "Correlations between human-coded and model-predicted body position durations across the entire long delay period. Correlations are provided within each posture and overall, and computed separately using group and individual models with and without outlier participants.")
```

@@

difference_plot <- function(ds) {
  ds <- mutate(ds, diff = prop_human - prop_model)
  ggplot(filter_outliers(ds), aes(x = pos, y = diff, color = pos, group = file)) +
  geom_rect(aes(xmin = "Held", xmax = "Upright",ymin = -.1, ymax = .1), fill = "#e5e5e5", color = "#e5e5e5") + 
  stat_summary(position = position_dodge(.4), alpha = .7) +
  stat_summary(data = filter(ds, file %in% outlier_files), position = position_dodge(.4), aes(shape = file), alpha = .7, color = "#333333") +
  scale_color_manual(values = pal, guide = "none") +
  scale_shape_discrete(guide = "none") + 
  coord_cartesian(ylim = c(-1, 1)) + xlab("") + 
  scale_y_continuous(name = "Prediction Difference (min)", breaks = seq(-1, 1, .2), labels = seq(-10, 10, 2), minor_breaks = waiver()) + 
    theme(axis.text.x = element_text(size = 13, color = "black"))
}
difference_plots <- map(agree_bins, ~ difference_plot(.x))
difference_plots <- map2(difference_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))
difference_plots[[1]] + difference_plots[[2]]
```

```{r pt2binstable}
#Bins
pt2corr_with_outliers <- map_dfc(agree_bins, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree_bins, ~ .x %>% filter_outliers %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr_bins <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

group_agree_cor <- cor_test(agree_bins$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree_bins$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree_bins$group %>% filter_outliers %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree_bins$split %>% filter_outliers %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr_bins)
pt2corr_bins <- bind_rows(pt2corr_bins, overall_row)
rm(overall_row)
apa_table(pt2corr_bins, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5, caption = "Correlations between human-coded and model-predicted body position durations using 10-minute bins during the long delay period. Correlations are provided within each posture and overall, and computed separately using group and individual models with and without outlier participants.")
```

```{r age, warning=FALSE, fig.cap="Age trends", fig.align="center", fig.width=5, fig.height=8}
fullday <- read_csv("data/imu-compiled.csv") %>% 
  mutate(id_uni = factor(id*100+session),
         group = factor(ifelse(age <= 8, "Younger", "Older")),
         nap_time = ifelse(is.na(sit_time), nap_time, NA))
fullday_long <- fullday %>% pivot_longer(cols = sit_time:upright_time, names_to = "position", values_to = "prop") %>% 
  mutate(position = factor(position,
                           levels = c("upright_time", "sit_time", "prone_time", "supine_time", "held_time"),
                           labels = c("Upright", "Sitting", "Prone", "Supine", "Held"))) %>% 
  arrange(position, age)

outlier_ids <- c(10701, 10401, 10601)
fullday %>% cor_mat(age, sit_time:upright_time) %>% cor_mark_significant()
fullday %>% filter(!(id_uni %in% outlier_ids)) %>% cor_mat(age, sit_time:upright_time) %>% cor_mark_significant()

fullday_long %>% drop_na(prop) %>% 
  ggplot() + facet_wrap("position", as.table = T, ncol = 2) + 
  geom_smooth(aes(x = age, y = prop), color = "darkgray", method = "lm", se = T) + 
  stat_summary(fun = "mean", mapping = aes(x = age, y = prop, group = id_uni, fill = position), shape = 21, size = .75) + 
  scale_fill_manual(values = pal, guide = "none") + 
  scale_x_continuous(name = "Age (months)", breaks = seq(3, 15, 3), limits = c(3,15)) + 
  ylim(0,1) + ylab("Proportion of waking day")

fullday_long %>% group_by(position, group) %>% get_summary_stats(prop)

### 2023-02-18 manuscript.tex
age graphs

\caption{Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant.}\label{fig:part2overall}
\end{figure}

@@

\caption{\label{tab:pt2overalltable}}

@@

\caption{\label{tab:part2bins}}

@@

\caption{Prediction performance (difference in minutes between human-coded and model-predicted body position) for 10-minute bins in the long delay period. Each point shows the mean and SE for a single participant for each body position, summarizing the prediction difference for each of their 10-minute bins. Points falling within the gray shaded region indicate that prediction errors were less than 1 minute. Performance is plotted separately for (A) group models and (B) individual models. The three outlier participants are plotted in dark gray, with a different shape marking each individual.}\label{fig:part2bins}
\end{figure}

@@

>>>>

\caption{Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant. The three outlier participants are plotted in dark gray, with a different shape marking each individual.}\label{fig:part2overall}
\end{figure}

@@

\caption{\label{tab:pt2overalltable}Correlations between human-coded and model-predicted body position durations across the entire long delay period. Correlations are provided within each posture and overall, and computed separately using group and individual models with and without outlier participants.}

@@

@@

\caption{Prediction performance (difference in minutes between human-coded and model-predicted body position) for 10-minute bins in the long delay period. Each point shows the mean and SE for a single participant for each body position, summarizing the prediction difference for each of their 10-minute bins. Points falling within the gray shaded region indicate that average prediction errors were less than 1 minute. Performance is plotted separately for (A) group models and (B) individual models. The three outlier participants are plotted in dark gray, with a different shape marking each individual.}\label{fig:part2bins}
\end{figure}

\caption{\label{tab:pt2binstable}Correlations between human-coded and model-predicted body position durations using 10-minute bins during the long delay period. Correlations are provided within each posture and overall, and computed separately using group and individual models with and without outlier participants.}

@@

{\centering \includegraphics{manuscript_files/figure-latex/timelines-1}

\caption{Timelines}\label{fig:timelines}
\end{figure}
